full title

### 2020-11-21 paper/pldi21/javascript.tex
Till Sec. 4.2

\section{Dynamic Shortcut for JavaScript}\label{sec:javascript}

In this section, we introduce the core language of JavaScript that supports
first-class functions, open objects, and first-class property names, and define
sealed symbolic execution of the core language for dynamic shortcut.

@@

States $\stset$ consist of labels $\labset$, memories $\memset$, contexts
$\ctxtset$, and environment addresses $\eaddrset$.  A memory $\mem \in \memset$
is a finite mapping from locations to values.  A context $\ctxt \in \ctxtset$ is
a finite mapping from environment addresses to tuple of environment addresses,
return labels, and left-hand side locations.  A location $\loc \in \locset$ is a
variable or an object property; a variable location consists of an environment
address and its name, and an object property location consists of an object
address and a string value.  A value $\val \in \valset$ is a primitive, an
address, or a function value.  An address $\addr \in \addrset$ is an environment
address or an object address.  A function value $\fval{x}{\lab} \in \fvalset$
consists of a parameter and a body label.  In the core language, the closed
scoping is used for functions for brevity thus only parameters and local
variables are accessible in the function body.

We formulate the concrete semantics of the core language.  The transition
relation between concrete states is defined with the semantics of references and
expressions using two different forms \fbox{$\referrule{\st}{\refer}{\loc}$} and
\fbox{$\exprrule{\st}{\expr}{\val}$}, respectively.  The initial states are
$\istset = \{ (\ilab, \varnothing, \epsilon, \tladdr) \}$ where $\ilab$ denotes
the initial label, $\epsilon$ empty map, and $\tladdr$ the top-level environment
address.  The function $\labnext$ returns the next label of a given label in the
current program $\prog$.

\subsection{Abstract Semantics}

In abstract semantics of the core language, we use the flow sensitivity with a
flow sensitive view abstraction $\fsviewmap: \labset \rightarrow \dom$ that
discriminates states using their labels: $\forall \lab \in \labset. \;
\fsviewmap(\lab) = \{ \st \in \stset \mid \st = (\lab, \_, \_, \_) \}$. Thus, the
sensitive abstract domain is defined as $\sabsdom = \labset \rightarrow
\absdom$.  We define an abstract state $\abselem \in \absdom$ as a tuple of an
abstract memory, an abstract context, an abstract address, and set of singleton
abstract addresses as follows:

\[
  \begin{array}{lr@{~}c@{~}l@{~}c@{~}l}
    \text{Abstract States} & \abselem &\in& \absdom &=& \absmemset \times \absctxtset
    \times \absaddrset \times \abscountset\\
    \text{Abstract Memories} & \absmem &\in& \absmemset &=& \abslocset \finmap
    \absvalset\\
    \text{Abstract Contexts} & \absctxt &\in& \absctxtset &=& \absaddrset \finmap
    \powerset{\absaddrset \times \viewset \times \powerset{\abslocset}}\\
    \text{Abstract Locations} & \absloc &\in& \abslocset &=& (\absaddrset \times
    \varset) \uplus (\absaddrset \times \strset)\\
    \text{Abstract Values} & \absval &\in& \absvalset &=& \powerset{\pvalset
    \uplus \absaddrset \uplus \fvalset}\\
    \text{Abstract Addresses} & \absaddr &\in& \absaddrset &=& \labset\\
    \text{Abstract Counters} & \abscount &\in& \abscountset &=& \absaddrset
    \rightarrow \{ \abszero, \absone, \absmany \}\\
  \end{array}
\]

An abstract memory $\absmem \in \absmemset$ is a finite mapping from abstract
locations $\abslocset$ to abstract values $\absvalset$.  Abstract locations
$\abslocset$ are pairs of abstract addresses with variable names or string
values. Abstract addresses $\absaddrset$ are defined with the
\textit{allocation-site abstraction} that partitions concrete addresses
$\addrset$ based on their allocation sites $\labset$.  Abstract contexts
$\absctxtset$ are finite maps from abstract addresses to powersets of triples of
abstract addresses, views, and powerset of abstract locations.  For abstract
counting~\cite{abstract-gc-counting, revisit-recency} in static analysis, we
define abstract counters $\abscountset$ that maps from abstract addresses to
their abstract counts representing how many times each abstract address has been
allocated; $\abszero$ denotes that it has never been allocated, $\absone$ once,
and $\absmany$ more than or equals to twice.

We define the semantics of view transition for the core language.  For abstract
memories, we use the notation $\absmem[L \mapstos \absval]$ to represent the
update of multiple abstract locations in $L$ with the abstract value $\absval$.
It performs the strong update if the abstract address for an abstract location
$(\absaddr, \_) \in L$ is singleton: $\abscount(\absaddr) = \absone$.
Otherwise, it performs the weak update for the soundness.  Moreover, we define
the increment function $\inc: \abscountset \times \absaddrset \rightarrow
\abscountset$ of the abstract counter defined as follows:
\[
  \inc(\abscount)(\absaddr_0) = \lambda \absaddr \in \absaddrset. \; \left\{
    \begin{array}{ll}
      \absone & \text{if} \; \absaddr = \absaddr_0 \wedge
      \abscount(\absaddr_0) = \abszero\\
      \absmany & \text{if} \; \absaddr = \absaddr_0 \wedge
      \abscount(\absaddr_0) = \absone\\
      \abscount(\absaddr) & \text{otherwise}
    \end{array}
  \right.
\]

>>>>

\section{Dynamic Shortcuts for JavaScript}\label{sec:javascript}
In this section, we introduce the core language of JavaScript that supports
first-class functions, open objects, and first-class property names, and define
sealed symbolic execution of the core language for dynamic shortcuts.
Due to the space limitation, we present the main design of the
language in this paper and refer the interested readers to a companion report~\cite{report}.

@@

States $\stset$ consist of labels $\labset$, memories $\memset$, contexts
$\ctxtset$, and environment addresses $\eaddrset$.  A memory $\mem \in \memset$
is a finite mapping from locations to values.  A context $\ctxt \in \ctxtset$ is
a finite mapping from environment addresses to tuple of environment addresses,
return labels, and left-hand side locations.  A location $\loc \in \locset$ is a
variable or an object property; a variable location consists of an environment
address and its name, and an object property location consists of an object
address and a string value.  A value $\val \in \valset$ is a primitive, an
address, or a function value.  An address $\addr \in \addrset$ is an environment
address or an object address.  A function value $\fval{x}{\lab} \in \fvalset$
consists of a parameter name and a body label.  In the core language, the closed
scoping is used for functions for brevity, thus only parameters and local
variables are accessible in a function body.

We formulate the concrete semantics of the core language.  The transition
relation between concrete states is defined with the semantics of references and
expressions using two different forms \fbox{$\referrule{\st}{\refer}{\loc}$} and
\fbox{$\exprrule{\st}{\expr}{\val}$}, respectively.  The initial states are
$\istset = \{ (\ilab, \varnothing, \epsilon, \tladdr) \}$ where $\ilab$ denotes
the initial label, $\epsilon$ empty map, and $\tladdr$ the top-level environment address.

\subsection{Abstract Semantics}
In the abstract semantics of the core language, we use the flow sensitivity with a
flow sensitive view abstraction $\fsviewmap: \labset \rightarrow \dom$ that
discriminates states using their labels: $\forall \lab \in \labset. \;
\fsviewmap(\lab) = \{ \st \in \stset \mid \st = (\lab, \_, \_, \_) \}$. Thus, the
sensitive abstract domain is defined as $\sabsdom = \labset \rightarrow
\absdom$.  We define an abstract state $\abselem \in \absdom$ as a tuple of an
abstract memory, an abstract context, an abstract address, and an
abstract counter as follows:

\[
  \begin{array}{l@{~}r@{~}c@{~}l@{~}c@{~}l}
\text{Abstract states} & \abselem &\in& \absdom &=& \absmemset \times \absctxtset
\times \absaddrset \times \abscountset\\
\text{Abstract memories} & \absmem &\in& \absmemset &=& \abslocset \finmap
\absvalset\\
\text{Abstract locations} & \absloc &\in& \abslocset &=& (\absaddrset \times
\varset) \uplus (\absaddrset \times \strset)\\
\text{Abstract addresses} & \absaddr &\in& \absaddrset &=& \labset\\
\text{Abstract contexts} & \absctxt &\in& \absctxtset &=& \absaddrset \finmap
\powerset{\absaddrset \times \viewset \times \powerset{\abslocset}}\\
\text{Abstract counters} & \abscount &\in& \abscountset &=& \absaddrset
\rightarrow \{ \abszero, \absone, \absmany \}\\
\text{Abstract values} & \absval &\in& \absvalset &=& \powerset{\pvalset
\uplus \absaddrset \uplus \fvalset}\\
  \end{array}
\]

An abstract memory $\absmem \in \absmemset$ is a finite mapping from abstract
locations $\abslocset$ to abstract values $\absvalset$.  Abstract locations
$\abslocset$ are pairs of abstract addresses with variable names or string
values. Abstract addresses $\absaddrset$ are defined with the
\textit{allocation-site abstraction} that partitions concrete addresses
$\addrset$ based on their allocation sites $\labset$.  Abstract contexts
$\absctxtset$ are finite maps from abstract addresses to powersets of triples of
abstract addresses, views, and powerset of abstract locations.  For abstract
counting~\cite{abstract-gc-counting, revisit-recency} in static analysis, we
define abstract counters $\abscountset$ that are mappings from abstract addresses to
their abstract counts representing how many times each abstract address has been
allocated; $\abszero$ denotes that it has never been allocated, $\absone$ once,
and $\absmany$ more than or equal to twice.

We define the semantics of the view transition for the core language.  For abstract
memories, we use the notation $\absmem[L \mapstos \absval]$ to represent the
update of multiple abstract locations in $L$ with the abstract value $\absval$.
It performs the strong update if the abstract address for an abstract location
$(\absaddr, \_) \in L$ is singleton: $\abscount(\absaddr) = \absone$.
Otherwise, it performs the weak update for the analysis soundness.  We use
the increment function $\inc: \abscountset \times \absaddrset \rightarrow
\abscountset$ of the abstract counter defined as follows:
\[
  \inc(\abscount)(\absaddr_0) = \lambda \absaddr \in \absaddrset. \; \left\{
    \begin{array}{ll}
      \absone & \text{if} \; \absaddr = \absaddr_0 \wedge
      \abscount(\absaddr_0) = \abszero\\
      \absmany & \text{if} \; \absaddr = \absaddr_0 \wedge
      \abscount(\absaddr_0) = \absone\\
      \abscount(\absaddr) & \text{otherwise}
    \end{array}
  \right.
\]
